{{< var titll >}}

### 2024-11-01 presentation.qmd
abc

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws1 <- laws_df1 
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::apsnn)
rsr <- selreport(ManifoldDestiny::aprhn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

@@

::: {.callout-note collapse="true"}
```{r}
#kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
```
:::

@@

::: {.callout-note collapse="true"}
```{r} 
#kable(laws2, format = "markdown", escape = FALSE)

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
library(ManifoldDestiny)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::apsnn)
rsr <- selreport(ManifoldDestiny::aprhn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

@@

::: {.callout-note collapse="true"}
```{r}
kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
```
:::

@@

::: {.callout-note collapse="true"}
```{r} 
kable(laws2, format = "markdown", escape = FALSE)
